RNeXML: Parsing and Serializing the Next Generation of Phyloinformatic Data in R

### 2014-06-26 manuscripts/manuscript.Rmd
typo fix
added SPARQL comment

The most powerful way to take advantage of the machine-readable nature
of the metadata involves the construction of SPARQL queries. This
approach can exploit the reasoning and logical deduction capacity of
formal vocabularies (ontologies). For a proper introduction to SPARQL
queries, see `r citet("Hartig Introduction to SPARQL")`.  Meanwhile, we just introduce the sytnax
necessary to apply such queries to NeXML files from R.  First we load
the necessary R library `r citep(citation("rrdf"))` and import the RDF-extracted metadata:

@@

We can then make arbitrary SPARQL queries directly from R.  For instance,
here is a simple query to extract the value of any `dc:title` element, analogous
to the XPath expression above:

>>>>

The most powerful way to take advantage of the machine-readable nature
of the metadata involves the construction of SPARQL queries. This
approach can exploit the reasoning and logical deduction capacity of
formal vocabularies (ontologies). For a proper introduction to SPARQL
queries, see `r citet("Hartig Introduction to SPARQL")`.  Meanwhile, we just introduce the syntax
necessary to apply such queries to NeXML files from R.  First we load
the necessary R library `r citep(citation("rrdf"))` and import the RDF-extracted metadata:

@@

<!-- it would be nice if we had a more persuasive example here. directly getting the value
of some predicate can be done the syntax-oriented way by treating the data as XML. what I
think we should be going for here is an example of a slightly more complex query that would
be painful to perform by scanning the XML document. I'm thinking of some sort of join of
multiple predicate values. Nothing great comes to mind yet, though... ->
We can then make arbitrary SPARQL queries directly from R.  For instance,
here is a simple query to extract the value of any `dc:title` element, analogous
to the XPath expression above:
